\subsection{HTTPS/SSL}
Why SSL is important.
\subsection{Full Disk Encryption}
What FDE is.
\subsubsection{Veracrypt}
How to work Veracrypt
\subsubsection{Luks}
How to work Luks
\subsection{Browser Extensions}
Let's make browsing more private!
\subsubsection{UBlock}
Blocks ad networks
\subsubsection{UMatrix}
Advanced: Blocks scripts and such
\subsubsection{NoScript}
Blocks all scripts on untrusted sites.
\subsubsection{Privacy Badger}
Blocks Trackers
\subsubsection{HTTPS Everywhere}
Enables SSL everywhere
\subsection{Encrypted Mobile Messaging}
Time to secure your mobile messages!
\subsubsection{Signal}
Signal requires phone, has good crypto.
\subsubsection{Viber/WhatsApp}
Uses Signal's crypto, owned privately and likely uses metadata.
\subsubsection{Telegram}
Snake oil in my opinion. Uses home-spun crypto.
\subsection{The Tor Browser}
What is Tor? How can you use it?
\subsection{VPNs}
Centralized Privacy by policy, not by design.
\subsection{Encrypted Messaging on Computers}
Secure those chats!
\subsubsection{Tox}
Peer-to-peer, not yet audited. 
\subsubsection{Riccochet}
Uses Tor to message with no metadata and no content.
\subsubsection{OTR}
Plug-in for XMPP.
\subsubsection{PGP}
Do yourself a favor and avoid this.
\subsection{Password Managers}
Online vs offline. Passwords in whose control?
\subsection{Operating Systems}
Avoid Windows. It's a spy machine.
\subsection{Data Minimization}
Good policy. Don't get it out there if it doesn't need to be.
\subsection{Compartmentalization}
Separate those identites!
